Fast radio burst cosmology: dispersion measure angular power spectrum

### 2015-01-20 writeup/dm_angular_ps.tex
Derivation of redshift clustering term.

The joint probablility of observing a pair of FRB events at 3D coordinates
$\vec x_i$ and $\vec x_j$ in infintessimal volumes $\ud^3\vec x_i$ and
$\ud^3\vec x_j$ is porportional to
\begin{equation}
    \calP(\vec x_i, \vec x_j) = \calP(\eta_i) \calP(\eta_j) \left[ 1 + b(z_i)
    b(z_j) \xi(\vec x_i - \vec x_j) \right] \frac{\ud^3\vec x_i}{\eta_i^2}
    \frac{\ud^3\vec x_j}{\eta_j^2}.
\end{equation}
The factors of $1/\eta^2$ are nessisary to achive the proper volume weighting,
a fact that can be seen by taking the limit of $\xi \to 0$ and integrating of
the angular coordinates.

An observed event has known angular coordinates, and we are interested in
correlations in $\Dne$ which is directly related to the line of sight
coordinate.  Fixing the angular coordinates:
\begin{equation}
    \calP(\eta_i, \eta_j | \hat{n}_i, \hat{n}_i) = N(\hat{n}_i, \hat{n}_i)
    \calP(\eta_i) \calP(\eta_j) \left[ 1 + b(z_i)
    b(z_j) \xi(\vec x_i - \vec x_j) \right] \ud \eta_i \ud \eta_j,
\end{equation}
where $N(\hat{n}_i, \hat{n}_i)$ is a normalizing factor which ensures the
expression integrates to unity over $\eta_i$ and $\eta_j$. \red{How to deal
with the $1/\eta^2$ factors?.}
Transforming to $\Dne$ as our distance measure, we obtain
\begin{equation}
\calP(\Dne_i, \Dne_j | \hat{n}_i, \hat{n}_i) = \calP(\eta_i, \eta_j |
\hat{n}_i, \hat{n}_i) \frac{\ud }{}
\end{equation}

>>>>

The joint probablility of observing a pair of FRB events at 3D coordinates
$\vec x_i$ and $\vec x_j$ in infintessimal volumes $\ud^3\vec x_i$ and
$\ud^3\vec x_j$ is porportional to
\begin{equation}
    \calP(\vec x_i, \vec x_j) = \calP(\eta_i) \calP(\eta_j) \left[ 1 + b(z_i)
    b(z_j) \xi(\vec x_i - \vec x_j) \right] \frac{\ud^3\vec x_i}{\eta_i^2}
    \frac{\ud^3\vec x_j}{\eta_j^2}.
\end{equation}
The factors of $1/\eta^2$ are nessisary to achive the proper volume weighting,
a fact that can be seen by taking the limit of $\xi \to 0$ and integrating of
the angular coordinates. Noting that $\calP(\eta_i)$ has units 
$({\rm MPc}\,{\rm rad}^2)^{-1}$.

An observed event has known angular coordinates, and we are interested in
correlations in $\Dne$ which is directly related to the line of sight
coordinate.  Fixing the angular coordinates:
\begin{equation}
    \calP(\eta_i, \eta_j | \hat{n}_i, \hat{n}_i) = N(\hat{n}_i, \hat{n}_i)
    \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
    b(z_j) \xi(\vec x_i - \vec x_j) \right] \ud \eta_i \ud \eta_j,
\end{equation}
where $N(\hat{n}_i, \hat{n}_i)$ is a normalizing factor which ensures the
expression integrates to unity over $\eta_i$ and $\eta_j$. The factors of
$1/\eta^2$ have been canceled when converting $\ud^3 \vec x = \eta^2 \ud \eta \ud^2
\vec \theta$. If the second term in brackets is small, then the normalizations
$N$ is 1 (since the distributions $\calP{\eta_i}$ are already normalized. 
This expression is
only valid if $i \ne j$.
Transforming to $\Dne$ as our distance measure, we obtain
\begin{align}
\calP(\Dne_i, \Dne_j | \hat{n}_i, \hat{n}_i)
    &= \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
        b(z_j) \xi(\vec x_i - \vec x_j) \right]
        \frac{\ud \eta_i}{\ud \Dne_i} \frac{\ud \eta_j}{\ud \Dne_j}
        \ud \Dne_i\ud \Dne_j
        \\
    &= \calP(\eta_i)\calP(\eta_j) \left[ 1 + b(z_i)
        b(z_j) \xi(\vec x_i - \vec x_j) \right]
        \frac{\ud \Dne_i}{1 + z_i}\frac{\ud \Dne_j}{1 + z_j}
\end{align}
Finally, taking the second moment and subtracting off the product of the first
moments:
\begin{equation}
\langle \Dne_i \Dne_j \rangle
    - \langle \Dne_i \rangle \langle \Dne_j \rangle =
    \int \Dne_i \Dne_j
    \frac{\calP(\eta_i)}{1 + z_i}\frac{\calP(\eta_j)}{1 + z_j}
    b(z_i) b(z_j) \xi(\vec x_i - \vec x_j)
        \ud \Dne_i\ud \Dne_j
\end{equation}
